\pkg{RProtoBuf}: Protocol Buffers for R

### 2010-02-26 papers/user2010/abstract.tex
another iteration on the abstract
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@295 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\title{\pkg{RProtoBuf}: Protocol Buffers for R }
\date{Abstract submitted for \textsl{useR! 2010}}

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}
  \addtolength{\parskip}{\baselineskip} 	% add a little vertical space
  \noindent % no ident for first paragraph
  Protocol buffers are a flexible, efficient, 
  automated mechanism for serializing structured data---think XML, but 
  smaller, faster, and simpler. 
  You define how you want your data to be structured once, then you can use 
  special generated source code to easily write and read your structured 
  data to and from a variety of data streams and using a 
  variety of officially supported languages---
  \proglang{Java}, \proglang{C++}, or \proglang{Python}---or 
  third party implementations for languages such as \proglang{C\#}, 
  \proglang{Perl}, \proglang{Ruby}, \proglang{Visual Basic}, and now 
  \proglang{R} via the \pkg{RProtoBuf} package.

  The \pkg{RProtoBuf} package implements R bindings to the C++
  protobuf library from Google. It uses features of the protocol 
  buffer library to support creation, manipulation, parsing and serialization
  of protocol buffers messages. The \pkg{RProtoBuf} package uses S4 classes
  and external pointers to expose objects that look and feel like standard 
  R lists, but constrained by the language agnostic definition of the 
  message type.

  \noindent \textbf{Keywords:}  
  \proglang{R}, \proglang{C++}, Serialization, Data Interchange
\end{abstract}
\end{document}

>>>>

\title{\pkg{RProtoBuf}: Protocol Buffers for R }
\date{Submitted to \textsl{useR! 2010}}

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}
  \addtolength{\parskip}{\baselineskip} 	% add a little vertical space
  \noindent % no ident for first paragraph
  %
  Protocol buffers are a flexible, efficient, automated mechanism for
  serializing structured data---think XML, but smaller, faster, and simpler.
  Users define how they want the data to be structured once in a
  \texttt{proto} file and then use special generated source code to easily
  write and read structured data to and from a variety of data streams and
  using a variety of officially supported languages--- \proglang{Java},
  \proglang{C++}, or \proglang{Python}---or third party implementations for
  languages such as \proglang{C\#}, \proglang{Perl}, \proglang{Ruby},
  \proglang{Haskell}, and now \proglang{R} via the \pkg{RProtoBuf} package.

  The \pkg{RProtoBuf} package implements \proglang{R} bindings to the
  \proglang{C++} protobuf library from Google. It uses features of the
  protocol buffer library to support creation, manipulation, parsing and
  serialization of protocol buffers messages. Taking advantage of facilities
  in the \pkg{Rcpp} package, \pkg{RProtoBuf} uses S4 classes and external
  pointers to expose objects that look and feel like standard \proglang{R}
  lists, but constrained by the language-agnostic definition of the message
  type.
  % [Dirk] what does that last half-sentence mean? constrained as in conforming

  % [Dirk] ok to add 'forward-looking' statements?
  As the protocal buffers library does not offer any built-in support
  for networked access to protocol buffer streams, we intend to take
  advantage on ongoing changes to the \proglang{R} system to expose a native
  \proglang{R} server. This is work-in-progress that we hope to report on at
  the conference.

  \noindent \textbf{Keywords:}  
  \proglang{R}, \proglang{C++}, Serialization, Data Interchange, Data Formats
\end{abstract}
\end{document}
